Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-06-26 thesis/introduction.tex
thesis w full ch2 draft

\begin{itemize}
\tightlist
\item
  \citet{fattahi+2013}, \citet{fattahi+2018}
\item
  \citet{sanchez-salcedo+hernandez2007}: mond in dsph
\item
  \citet{mayer+2001} theory of tidal stripping
\item
  \citet{IH1995} structural parameters
\end{itemize}

@@

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/mw_satellites_ongaia.pdf}}
\caption[Dwarf galaxies sky position]{The location of MW dwarf galaxies
on the sky. Dwarf galaxies are taken as confirmed dwarfs with MW or LMC
hosts from the \citet{pace2024} catalogue (version 1.0.3. We label all
classical dwarfs and the Magellanic clouds, changing symbols based on
the relevance to this work (classical dwarfs, Magellanic clouds REF, and
the systems in question or comparison). \textbf{TODO: use
abbreviations}}
\end{figure}

\subsection{Cosmological context}\label{cosmological-context}

@@

\subsection{Theoretical Background}\label{theoretical-background}

@@

An emperical estimate of where the simulation's stars are becoming
unbound is, as stated in \citet{PNM2008}, the break radius
\begin{equation}
R_b = C\,\sigma_{v}\,\Delta t
\end{equation} where \(\sigma_v\) is the present line of sight velocity
dispersion , \(\delta t\) is the time since pericentre, and
\(C \approx 0.55\) is a fit. The idea motivating this equation is stars
in the inner regions will have dynamically equilibriated to the new
potential (phase mixed), however the outer regions are no longer in
steady state, so we have to wait until the crossing time reaches them as
well.

As illustrated in fig.~\ref{fig:toy_profiles}, the density profile
initially stars off exponential. At increasing times since the first
pericentric passage, the break radius, appearing as an apparent
separation between the slopes of the inner and outer profile, increases.

@@

@@

From the \citet{nfw1996} paper, eqns. 3 \& 4 \begin{equation}
\frac{\rho}{\rho_c} = \frac{\delta_c}{(r/r_s)(1+r/r_s)^2}
\end{equation} where \begin{equation}
\delta_c = \frac{200}{3}\frac{c^3}{[\ln(1+c)-c/(1+c)]}
\end{equation} \(c\) is concentration parameter, \(\rho_c\) is the
critical density of the universe, and \(r_s\) is the characteristic
scale length of the halo.

The NFW halo is sometimes described by \(M_{200}\). \(r_{200}\) is the
radius at which the mean density of the halo interior to \(r_{200}\) is
200 times the critical density of the universe, and \(M_{200}\) is the
mass contained inside \(r_{200}\). As equations: \begin{equation}
\rho_{200} = 200\rho_{c} = \frac{M_{200}}{(4\pi/3) r_{200}^3}
\end{equation}

\begin{equation}
r_{200} = \sqrt[3]{\frac{1}{200}\frac{3M_{200}}{4\pi \rho_{\rm c
}}}
\end{equation}

\begin{equation}
M_{200} = \frac{4\pi}{3} r_{200}^3\ \rho_{200}
\end{equation}

\(M_{200}\) is also sometimes called the virial mass of the halo.
\(r_{200}\) is directly related to \(r_s\) by \begin{equation}
r_{200} = c\,r_s
\end{equation}

Another useful definition is \begin{equation}
A(x) \equiv \log (1+x) - \frac{x}{1+x}.
\end{equation}

We will also define a dimensionless radius \begin{equation}
x \equiv r/r_s.
\end{equation}

A simple substitution to the definition gives

\begin{equation}
\rho(x) =  \frac{\rho_s/3}{x\ (1+x)^2}
\end{equation} where \begin{equation}
\rho_s = \frac{c^3}{A(c)} \rho_{200}
\end{equation} and \(A(c)\) is as above. The characteristic density can
also be written in terms of scale mass, \(M_s = M_{200}/{A(c)}\) (see
below), giving \begin{equation}
\rho_s = \frac{c^3}{A(c)} \frac{M_{200}}{(4\pi/3)\ r_{200}^3}  = \frac{3M_s}{4\pi\, {r_s}^3}
\end{equation} Note that the NFW density profile is the same as an
alpha-beta-gamma profile where \(\alpha=\gamma=1\) and \(\beta =3\).

\subsubsection{Circular velocity}\label{circular-velocity}

The circular velocity in terms of
\(v_{200} = \sqrt{G M_{200} / R_{200}}\) is \begin{equation}
\left(v_{\rm circ}/v_{200}\right)^2 = \frac{A(x)/x}{A(c)/c},
\end{equation}

or in terms of \(M_s\) and \(r_s\), \begin{equation}
v_{\rm circ}^2 = \frac{G M(r)}{r} = \frac{G M_s A(r/r_s)}{r}.
\end{equation} Another parameterization of the NFW profile is in terms
of the maximum circular velocity \(v_{\rm circ}^{\rm max}\) and the
radius at which it is reached \(r_{\rm circ}^{\rm max}\). Given the
scale radius, \begin{equation}
r_{\rm circ}^{\rm max} = \alpha\ r_s
\end{equation}

>>>>

\begin{itemize}
\tightlist
\item
  \citet{fattahi+2013}, \citet{fattahi+2018}
\item
  \citet{sanchez-salcedo+hernandez2007}: mond in dsph
\item
  \citet{mayer+2001} theory of tidal stripping
\item
  \citet{IH1995} structural parameters
\item
  \citet{mateo1998}, \citet{simon2019} ARAA on ultrafaints.
\item
  \citet{walker+penarrubia2011}: measuring cores and cusps
\item
  \citet{battaglia+nipoti2022}: dynamics and dwarf galaxies review
\item
  \citet{dsouza+bell2022}, \citet{santistevan+2024}. challenges to
  backwards time integration
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics[width=5.41667in,height=\textheight,keepaspectratio]{figures/mw_satellites_onsky_scl_umi_for_1.pdf}
\caption[Dwarf galaxies sky position]{The location of MW dwarf galaxies
on the sky. Dwarf galaxies are taken as confirmed dwarfs with MW or LMC
hosts from the \citet{pace2024} catalogue (version 1.0.3. We label all
classical dwarfs and the Magellanic clouds, changing symbols based on
the relevance to this work (classical dwarfs, Magellanic clouds REF, and
the systems in question or comparison). The background image is from
ESA/Gaia/DPAC
(https://www.esa.int/ESA\_Multimedia/Images/2018/04/Gaia\_s\_sky\_in\_colour2).}\label{fig:mw_satellite_system}
\end{figure}

\subsection{Motivation}\label{motivation}

\begin{itemize}
\tightlist
\item
  Sculptor and Ursa Minor are possibly unusual.
\end{itemize}

\section{Cosmological context}\label{cosmological-context}

@@

Origin of NFW profiles

\section{Theoretical Background}\label{theoretical-background}

@@

An emperical estimate of where the simulation's stars are becoming
unbound is, as stated in \citet{PNM2008}, the break radius
\begin{equation}{
R_b = C\,\sigma_{v}\,\Delta t
}\end{equation} where \(\sigma_v\) is the present line of sight velocity
dispersion , \(\delta t\) is the time since pericentre, and
\(C \approx 0.55\) is a fit. The idea motivating this equation is stars
in the inner regions will have dynamically equilibriated to the new
potential (phase mixed), however the outer regions are no longer in
steady state, so we have to wait until the crossing time reaches them as
well.

As illustrated in Fig.~\ref{fig:toy_profiles}, the density profile
initially stars off exponential. At increasing times since the first
pericentric passage, the break radius, appearing as an apparent
separation between the slopes of the inner and outer profile, increases.

@@

\subsubsection{Background}\label{background}

\subsubsection{The N-body method}\label{the-n-body-method}

\begin{itemize}
\tightlist
\item
  Nbody as a solution to the collisionless boltzman equation
\item
  limitations and interpretation (MC sampling of phase space)
\item
  Tree approximations and the BH method
\end{itemize}

\subsection{Tidal effects on dark matter
halos}\label{tidal-effects-on-dark-matter-halos}

\begin{itemize}
\tightlist
\item
  EN2020 tidal tracks
\item
  peñarrubia2009/etc.
\item
  assumtions and limitations
\end{itemize}

@@

\subsubsection{NFW}\label{nfw}

From \citet{nfw1996}, eqns. 3 \& 4 \begin{equation}{
\frac{\rho}{\rho_c} = \frac{\delta_c}{(r/r_s)(1+r/r_s)^2}
}\end{equation} where \begin{equation}{
\delta_c = \frac{200}{3}\frac{c^3}{[\ln(1+c)-c/(1+c)]}
}\end{equation} \(c\) is concentration parameter, \(\rho_c\) is the
critical density of the universe, and \(r_s\) is the characteristic
scale length of the halo.

The NFW halo is sometimes described by \(M_{200}\). \(r_{200}\) is the
radius at which the mean density of the halo interior to \(r_{200}\) is
200 times the critical density of the universe, and \(M_{200}\) is the
mass contained inside \(r_{200}\). As equations: \begin{equation}{
\rho_{200} = 200\rho_{c} = \frac{M_{200}}{(4\pi/3) r_{200}^3}
}\end{equation}

\begin{equation}{
r_{200} = \sqrt[3]{\frac{1}{200}\frac{3M_{200}}{4\pi \rho_{\rm c
}}}
}\end{equation}

\begin{equation}{
M_{200} = \frac{4\pi}{3} r_{200}^3\ \rho_{200}
}\end{equation}

\(M_{200}\) is also sometimes called the virial mass of the halo.
\(r_{200}\) is directly related to \(r_s\) by \begin{equation}{
r_{200} = c\,r_s
}\end{equation}

The circular velocity in terms of
\(v_{200} = \sqrt{G M_{200} / R_{200}}\) is \begin{equation}{
\left(v_{\rm circ}/v_{200}\right)^2 = \frac{A(x)/x}{A(c)/c},
}\end{equation}

or in terms of \(M_s\) and \(r_s\), \begin{equation}{
v_{\rm circ}^2 = \frac{G M(r)}{r} = \frac{G M_s A(r/r_s)}{r}.
}\end{equation} Another parameterization of the NFW profile is in terms
of the maximum circular velocity \(v_{\rm circ}^{\rm max}\) and the
radius at which it is reached \(r_{\rm circ}^{\rm max}\). Given the
scale radius, \begin{equation}{
r_{\rm circ}^{\rm max} = \alpha\ r_s
}\end{equation}

### 2025-06-26 thesis/methods.tex
thesis w full ch2 draft

fig.~\ref{fig:v_circ_potential} plots the circular velocity profiles of
each component of our fiducially potential. We adopt the potential
described in \citet{EP2020}, an analytic approximation of
\citet{mcmillan2011}. The potential consisting of a stellar Bulge, a
thin and thick disk, and a dark matter NFW halo. Especially in the
regime where Sculptor and Ursa Minor orbit, the dark matter halo is the
dominant component of the potential. The details of the stellar disk and
bulge are less important.

@@

\begin{equation}
\Phi(r) = - \frac{GM}{r + a}
\end{equation} where \(a=1.3\,{\rm kpc}\) is the scale radius and
\(M=2.1 \times 10^{10}\,\Mo\) is the total mass.

The thin and thick disks are represented with the
\citet{miyamoto+nagai1975} cylindrical potential: \begin{equation}
\Phi(R, z) = \frac{-GM}{\left(R^2 + \left[a + \sqrt{z^2 + b^2}\right]^{2}\right)^{1/2}}
\end{equation}

@@

Finally, in chapter REF, we consider the influence of the large Milky
Cloud on the orbits and evolution of Scl. We adopt the
\citet{vasiliev2024} multipole approximation of an N-body simulation of
the LMC and MW. Their initial conditions are

@@

We use Agama \citep{agama} to generate initial conditions. We initially
assume galaxies are described by an NFW dark matter potential (REF) and
the stars are merely collisionless tracers embedded in this potential
(added on in post-processing). The density is exponentially truncated
with a profile
\begin{equation}\protect\phantomsection\label{eq:trunc_nfw}{
\rho_{\rm tNFW} = e^{-r/r_t}\ \rho_{\rm NFW}(t)
}\end{equation} where we adopt \(r_t = 100 r_s\) or approximately 10
times \(r_{200}\).

@@

To ensure that the initial conditionss of the simulation are dynamically
relaxed and well-converged, we run the simulation in isolation (no
external potential) for 5 Gyr (or approximately the crossing timescale).
Our fiducial isolation halo uses \(r_s=2.76\) kpc and
\(M_s = 0.29 \times 10^{10}\) Msun, but can be easily rescaled for any
length or mass scale.

We adopt a softening length of \begin{equation}
h_{\rm grav} = 0.014 \left(\frac{r_s}{2.76\,{\rm kpc}}\right)\left(\frac{N}{10^7}\right)^{-1/2}.
\end{equation} See appendix REF for a discussion of this choice, which
is similar to the \citet{power+2003} suggested softening.

@@

As discussed in \citet{power+2003}, the region where density is
converged is related to the region which becomes collisionally relaxed
over the time of the universe (so about 5-10 Gyr). (i.e.~where the
collisionless assumption breaks down). The relaxation timescale is given
by \(t_{\rm relax} = t_{\rm circ} N(r) / 8\ln N(r)\) or otherwise,
\begin{equation}
t_{\rm relax}(r) := t_{\rm circ}(r) \frac{N(r)}{8\,\ln N(r)}
= {t_{\rm circ}(r_{200})} \frac{\sqrt{200}}{8} \frac{N(r)}{\ln N(r)} \left(\frac{\bar \rho (r)}{\rho_{\textrm crit}}\right)^{-1/2}
\end{equation} This works out to be about 6-10 times (increasing with
particle number) our adopted softening length for NFW halos given our
assumptions. As such, at full resolution, we can only trust density
profiles down to \(\sim10\epsilon\), just enough to resolve stellar
density profiles.

@@

\begin{equation}
v_{\rm circ}(r) = \sqrt{\frac{GM(r)}{r}}
\end{equation}

@@

Let \(\Psi\) be the potential (normalized to vanish at infinity) and
\({\cal E}\) is the binding energy \({\cal E} = \Psi - 1/2 v^2\). If we
know \(f({\cal E})\), the distribution function (phase-space density in
energy), then we assign the stellar weight for a given particle with
energy \({\cal E}\) is \begin{equation}
P_\star({\cal E}) = \frac{f_\star({\cal E})}{f_{\rm halo}({\cal E})}.
\end{equation} While \(f({\cal E})\) is a phase-space density, the
differential energy distribution includes an additional \(g({\cal E})\)
occupation term (BTXXX).

We use Eddington inversion to find the distribution function, (eq.
4-140b in BT87) \begin{equation}
f({\cal E}) = \frac{1}{\sqrt{8}\, \pi^2}\left( \int_0^{\cal E} \frac{d^2\rho}{d\Psi^2} \frac{1}{\sqrt{{\cal E} - \Psi}}\ d\Psi + \frac{1}{\sqrt{\cal E}} \left(\frac{d\rho}{d\Psi}\right)_{\Psi=0} \right).
\end{equation}

@@

Perhaps the simplest in form, the 2D exponential is commonly used to
describe dwarf galaxy's density profiles as well as stellar disks. The
stellar profile is given by \begin{equation}
\Sigma_\star(R) = A e^{-R / R_s}
\end{equation} where \(A\) is the normalization and \(R_s\) is the
exponential scale radius. The 3D deprojected profile is found through
Abel inversion \citep[e.g.][]{errani+2024}: \begin{equation}
\rho_\star (r) =- \frac{1}{\pi}\int_r^\infty \frac{d\Sigma}{dR} \frac{1}{\sqrt{R^2 - r^2}} dR  = \frac{\Sigma_0}{\pi R_s^2}\,K_0(r/R_s)
\end{equation} where \(K_0\) is the 0th order modified Bessel function
of the second type.

@@

The Plummer density profile is generally considered to be a reasonable
empirical fit to Globular Clusters, where it was first proposed
\citep{sadfjk}. Plummer profiles are also sometimes used to describe
dwarf spheroidal galaxies REFS and galactic bulges REF. A Plummer
profile is defined by \begin{equation}
\Sigma(R) = \frac{M}{4\pi R_s^2} \left(1 + \frac{R^2}{R_s^2}\right)^{-2} ,
\end{equation} where \(M\) is the total mass and \(R_s\) is the
characteristic scale radius. The 3D density is \begin{equation}
\rho(r) = \frac{3M}{4\pi\,R_s^3} \left(1 + \frac{r^2}{R_s^2}\right)^{-5/2}.
\end{equation}

@@

\citet{power+2003} suggest the empirical rule that the ideal softening
(balancing integration time and only compromising resolution in
collisional regime) is \begin{equation}
h_{grav} = 4 \frac{R_{200}}{\sqrt{N_{200}}}
\end{equation}

>>>>

Fig.~\ref{fig:v_circ_potential} plots the circular velocity profiles of
each component of our fiducially potential. We adopt the potential
described in \citet{EP2020}, an analytic approximation of
\citet{mcmillan2011}. The potential consisting of a stellar Bulge, a
thin and thick disk, and a dark matter NFW halo. Especially in the
regime where Sculptor and Ursa Minor orbit, the dark matter halo is the
dominant component of the potential. The details of the stellar disk and
bulge are less important.

@@

\begin{equation}{
\Phi(r) = - \frac{GM}{r + a}
}\end{equation} where \(a=1.3\,{\rm kpc}\) is the scale radius and
\(M=2.1 \times 10^{10}\,\Mo\) is the total mass.

The thin and thick disks are represented with the
\citet{miyamoto+nagai1975} cylindrical potential: \begin{equation}{
\Phi(R, z) = \frac{-GM}{\left(R^2 + \left[a + \sqrt{z^2 + b^2}\right]^{2}\right)^{1/2}}
}\end{equation}

@@

Finally, we also consider the influence of the large Milky Cloud on the
orbits and evolution of Scl. We adopt the \citet{vasiliev2024} multipole
approximation of an N-body simulation of the LMC and MW. Their initial
conditions are

@@

We use Agama \citep{agama} to generate initial conditions. We initially
assume galaxies are described by an NFW dark matter potential (REF) and
the stars are merely collisionless tracers embedded in this potential
(added on in post-processing). The density is a cubic-exponentially
truncated with a profile
\begin{equation}\protect\phantomsection\label{eq:trunc_nfw}{
\rho_{\rm tNFW} = e^{-(r/r_t)^3}\ \rho_{\rm NFW}(t)
}\end{equation} where we adopt \(r_t = 20 r_s\) or approximately
\(r_{200}\) for our Sculptor-like fiducial halo. (Using \(r_{200}\)
depends on the chosen scale of the halo, we chose to be scale free
here.) This truncation causes the density to drop quickly past
\(20 r_s\) but retails \textgreater{} 90 \(\%\) agreement with an NFW
within \(18r_s\). This choice is purely for numerical convenience,
however it is unlikely that the outer density profile of loosely bound
particles past \(20\) kpc affects the evolution of the halo. A more
detailed cosmological consideration would be ideal.

@@

To ensure that the initial conditionss of the simulation are dynamically
relaxed and well-converged, we run the simulation in isolation (no
external potential) for 5 Gyr (or about 3 times the crossing timescale
at the virial radius). Our fiducial isolation halo uses \(r_s=2.76\) kpc
and \(M_s = 0.29 \times 10^{10}\) Msun, but can be easily rescaled for
any length or mass scale.

We adopt a softening length of \begin{equation}{
h_{\rm grav} = 0.014 \left(\frac{r_s}{2.76\,{\rm kpc}}\right)\left(\frac{N}{10^7}\right)^{-1/2}.
}\end{equation} See appendix REF for a discussion of this choice, which
is similar to the \citet{power+2003} suggested softening.

@@

As discussed in \citet{power+2003}, the region where density is
converged is related to the region which becomes collisionally relaxed
over the time of the universe (so about 5-10 Gyr). (i.e.~where the
collisionless assumption breaks down). The relaxation timescale is given
by \(t_{\rm relax} = t_{\rm circ} N(r) / 8\ln N(r)\) or otherwise,
\begin{equation}{
t_{\rm relax}(r) := t_{\rm circ}(r) \frac{N(r)}{8\,\ln N(r)}
= {t_{\rm circ}(r_{200})} \frac{\sqrt{200}}{8} \frac{N(r)}{\ln N(r)} \left(\frac{\bar \rho (r)}{\rho_{\textrm crit}}\right)^{-1/2}
}\end{equation} This works out to be about 6-10 times (increasing with
particle number) our adopted softening length for NFW halos given our
assumptions. As such, at full resolution, we can only trust density
profiles down to \(\sim10\epsilon\), just enough to resolve stellar
density profiles.

@@

\begin{equation}{
v_{\rm circ}(r) = \sqrt{\frac{GM(r)}{r}}
}\end{equation}

@@

Let \(\Psi\) be the potential (normalized to vanish at infinity) and
\({\cal E}\) is the binding energy \({\cal E} = \Psi - 1/2 v^2\). If we
know \(f({\cal E})\), the distribution function (phase-space density in
energy), then we assign the stellar weight for a given particle with
energy \({\cal E}\) is \begin{equation}{
P_\star({\cal E}) = \frac{f_\star({\cal E})}{f_{\rm halo}({\cal E})}.
}\end{equation} While \(f({\cal E})\) is a phase-space density, the
differential energy distribution includes an additional \(g({\cal E})\)
occupation term (BTXXX).

We use Eddington inversion to find the distribution function, (eq.
4-140b in BT87) \begin{equation}{
f({\cal E}) = \frac{1}{\sqrt{8}\, \pi^2}\left( \int_0^{\cal E} \frac{d^2\rho}{d\Psi^2} \frac{1}{\sqrt{{\cal E} - \Psi}}\ d\Psi + \frac{1}{\sqrt{\cal E}} \left(\frac{d\rho}{d\Psi}\right)_{\Psi=0} \right).
}\end{equation}

@@

Perhaps the simplest in form, the 2D exponential is commonly used to
describe dwarf galaxy's density profiles as well as stellar disks. The
stellar profile is given by \begin{equation}{
\Sigma_\star(R) = A e^{-R / R_s}
}\end{equation} where \(A\) is the normalization and \(R_s\) is the
exponential scale radius. The 3D deprojected profile is found through
Abel inversion \citep[e.g.][]{errani+2024}: \begin{equation}{
\rho_\star (r) =- \frac{1}{\pi}\int_r^\infty \frac{d\Sigma}{dR} \frac{1}{\sqrt{R^2 - r^2}} dR  = \frac{\Sigma_0}{\pi R_s^2}\,K_0(r/R_s)
}\end{equation} where \(K_0\) is the 0th order modified Bessel function
of the second type.

@@

The Plummer density profile is generally considered to be a reasonable
empirical fit to Globular Clusters, where it was first proposed
\citep{sadfjk}. Plummer profiles are also sometimes used to describe
dwarf spheroidal galaxies REFS and galactic bulges REF. A Plummer
profile is defined by \begin{equation}{
\Sigma(R) = \frac{M}{4\pi R_s^2} \left(1 + \frac{R^2}{R_s^2}\right)^{-2} ,
}\end{equation} where \(M\) is the total mass and \(R_s\) is the
characteristic scale radius. The 3D density is \begin{equation}{
\rho(r) = \frac{3M}{4\pi\,R_s^3} \left(1 + \frac{r^2}{R_s^2}\right)^{-5/2}.
}\end{equation}

@@

\citet{power+2003} suggest the empirical rule that the ideal softening
(balancing integration time and only compromising resolution in
collisional regime) is \begin{equation}{
h_{grav} = 4 \frac{R_{200}}{\sqrt{N_{200}}}
}\end{equation}

### 2025-06-26 thesis/sculptor.tex
thesis w full ch2 draft

@@

fig.~\ref{fig:unref} contains example orbits

@@

As discussed in \citet{battaglia+2022}, Sculptor's orbit is strongly
influenced by the presence of an LMC. Figure
fig.~\ref{fig:scl_lmc_orbit_effect}, the addition of an LMC reduces
Scl's pericentre with the MW and implies that Scl may be on its first
infall with the MW, in contrast to the discussion above. Thus, the LMC
has a critical impact on the evolution of Scl. Additionally, Scl passes
rapidly but relatively close to the LMC in the past 100 Myr.

>>>>

\subsection{Derived properties}\label{derived-properties}

\begin{table*}[t]
\centering
\begin{tabular}{lll}
\toprule
parameter & value & reference\\
\midrule
$L_\star$ & $1.82_{-0.22}^{+0.25}\times10^6\ L_\odot$ & \\
$M_\star$ & $2.7_{-0.6}^{+0.7} \times10^6\ {\rm M}_\odot$ & \\
$M_{200}$ & $0.48_{-0.25}^{+0.52}\ M_0$ & \\
$c_{\rm NFW}$ & $13.1_{-2.8}^{+3.6}$ & \\
$v_{\rm circ, max}$ & $31\pm8\,\kms$ & \\
$r_{\rm circ, max}$ & $5.9 \pm 2.9$ kpc & \\
$r_{\rm break, obs}$ & $25 \pm 5$ arcmin & \\
$t_{\rm break, obs}$ & $110\pm30$ Myr & \\
\bottomrule
\end{tabular}
\end{table*}

@@

Fig.~\ref{fig:unref} contains example orbits

@@

As discussed in \citet{battaglia+2022}, Sculptor's orbit is strongly
influenced by the presence of an LMC. Figure
Fig.~\ref{fig:scl_lmc_orbit_effect}, the addition of an LMC reduces
Scl's pericentre with the MW and implies that Scl may be on its first
infall with the MW, in contrast to the discussion above. Thus, the LMC
has a critical impact on the evolution of Scl. Additionally, Scl passes
rapidly but relatively close to the LMC in the past 100 Myr.
